\documentclass{ylcv}
\usepackage[encapsulated]{CJK}
\newcommand\myCJK[1]{\begin{CJK}{UTF8}{gbsn}
						 #1
\end{CJK}}
\usepackage{hyperref}
\begin{document}
\NAME{Zhejian \textbf{YU}}
\EMAIL{Zhejian.19@intl.zju.edu.cn}
\TEL{+86 18006848198}
\maketitle

% This CV is also available at \url{https://yuzjlab.github.io/CV/}.

\section{Contact}
Personal E-Mail: \texttt{yuzhejian2001@gmail.com}\par
E-Mail for School: \texttt{Zhejian.19@intl.zju.edu.cn}\par
E-Mail for School: \texttt{3190110679@zju.edu.cn}\par
E-Mail for School: \texttt{s2009764@ed.ac.uk}

\section{Education}

\subsection[09/2019--now]{Zhejiang University-University of Edinburgh Institute}

Biomedical Informatics major with ZJU GPA 3.71

\section{Personal Projects}

All following projects are available at:

\begin{itemize}
	\item GitHub: \url{https://github.com/YuZJLab}
	\item Gitee: \url{https://gitee.com/YuZJLab}
\end{itemize}

You may also find me on LeetCode: \url{https://leetcode-cn.com/u/yuzj/}.

\subsection[08/04/2020--now]{BioDocker (Docker)}

\begin{itemize}
	\item Independent Docker project aimed at building frequently-used Docker images. Available from \url{https://gitee.com/yuzjlab/BioDocker}.
\end{itemize}

\subsection[01/06/2020--now]{Java Algorithms (Java)}

\begin{itemize}
	\item Java implementation of useful algorithms and data structures. Available from \url{https://gitee.com/yuzjlab/java_algorithms}.
\end{itemize}

\subsection[12/23/2019--now]{LinuxMiniPrograms (Asciidoctor, Bash, C, Python, PowerShell)}

\begin{itemize}
	\item Independent Bash project aimed at simplifying daily system administration tasks. Available from \url{https://gitee.com/yuzjlab/LinuxMiniPrograms}.
	\item \verb|AutoZip| is a (de)compress utility which can create and extract archive of multiple format with simple syntax.
	\item \verb|LiveChat| is a chatting server which allows multiple users to chat via ssh.
	\item \verb|lib| contains \verb|libdo| which can produce a informative log when executing jobs on a cluster with job systems like OpenPBS, Torque or IBM LSF Systems.
\end{itemize}

\subsection[09/01/2021--29/01/2021]{PyCOVID (Python, SQLite)}

\begin{itemize}
	\item A COVID-19 data visualizer using Python and SQLite with COVID-19 Hunter Award. Available from \url{https://gitee.com/yuzjlab/PyCOVID}.
	\item Demo video available at \url{https://www.bilibili.com/video/BV1aX4y1N74j?p=1}.
\end{itemize}

\subsection[03/11/2020--30/05/2021]{R Cheatsheet (\LaTeX, RMarkdown)}

\begin{itemize}
	\item R Cheatsheet from Applied Data Science 2. Available from \url{https://gitee.com/yuzjlab/R_CheatSheet}.
\end{itemize}

\subsection[04/11/2020-08/13/2020]{SoftInstall (\LaTeX)}

\begin{itemize}
	\item Independent project aiming at creating a database of frequently used bioinformatics software and their installation methods. Available from \url{https://gitee.com/yuzjlab/SoftInstall}
\end{itemize}

\subsection[01/06/2020--now]{YLBook.cls (\LaTeX)}

\begin{itemize}
	\item Independent \LaTeX templates. Available from \url{https://gitee.com/yuzjlab/YLBook.cls}.
	\item \verb|ylarticle| and \verb|ylcollection| is based on Stylish Article available from \url{http://www.latextemplates.com/}. \verb|ylbook| and \verb|ylcv| (The template of this CV) is independent.
	\item Changes: Despite from some changes in format, ``web'' option was added to make them suitable to desktop readers.
\end{itemize}

\section{Research Experience}

\subsection[03/03/2020--11/16/2020]{\myCJK{罕见增生性胃息肉原位复发的机理研究}}

(Mechanism Studies of Rare Recurrent Hypertrophic Gastric Pollyps)

\begin{itemize}
	\item University-level SRTP guided by professor Wei GUO with number X20200492.
	\item Build and maintain bioinformatics analysis pipelines on computing clusters provided by Zhejiang University International Campus.
	\item Perform mutation (SNP, Indel) calling from DNA data generated by second generation sequencing.
	\item Code available from \url{https://gitee.com/yuzjlab/DNA-Mutation-Calling}.
\end{itemize}

\section{Skills}

\begin{description}
	\item[BioInformatics] Able to use Next-Generation Sequencing (NGS) DNA sequence analysis tools for somatic or germline Single-Nucleotide Variants (SNVs) or indels like BWA, GATK, SamTools, VCFTools and many more. Able to work with multiple variant callers like GATK, LoFreq, Illumina Manta, Illumina Strelka, MuTect2, Shimmer and Varscan. Able to perform variant annotation using AnnoVar.
	\item[Language] Mandarin (native), English (CET6=534).
	\item[Programming] Asciidoctor, Bash, Docker, Java, \LaTeX, SQL, Python and R.
	\item[SysAdmin] SysAdmin skills required to work at UNIX-like operating systems. Including:
	\begin{itemize}
		\item[Systems] Work experience on systems built on CentOS, Debian, Ubuntu and FreeBSD.
		\item[Database] Manipulate data in PostgreSQL, SQLite and MySQL using SQL.
		\item[Remote] Work remotely using SSH, SCP or Telnet. Use Text User-Intercace (TUI) text editors like VIM and GNU EMACS.
		\item[Software] Operate package-management systems like APT, DNF, AnaConda or LinuxBrew. Compile programs using GNU Toolchain including \verb|autoconf|, GNU Make, CMake, GNU Compiler Collection (GCC) or Clang.
		\item[Server] Set up basic FTP server using VSFTPD or Pure-FTPD. Set up basic websites with Java servlets and Apache or Nginx HTTP server. Manage services using systemctl. Operate containers with Docker.
		\item[Clustering] Work with clusters using OpenPBS, Torque or IBM LSF Systems. Set up distributed file systems like GlusterFS.
	\end{itemize}
\end{description}

\end{document}
